---
title: "Visualizing uncertainty and creating pretty tables"
date: "Assigned 2/20/19, Due 2/27/19"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: "journal"
    css: "website-custom.css"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = FALSE,
                      dev.args = list(bg="transparent"))

```

## Background
For this homework we will again use data from [kaggle](https://www.kaggle.com), this time looking at [crime rates in Denver, CO](https://www.kaggle.com/paultimothymooney/denver-crime-data). 

#### Getting Started
You can download the data we'll use for this homework either [from kaggle](https://www.kaggle.com/paultimothymooney/denver-crime-data) or from canvas. Please visit the aforementioned link for a description of the data. We will be using the `crime.csv` file. Note that if you do download the data directly from kaggle your plots may not match mine exactly, given that the data are updated daily.

## Assignment
1. Select rows corresponding to a crime and reproduce the following plot. Note that because these are proportion data, I used the following formula to calculate the standard error $\sqrt{(p(1-p) / n}$.

```{r echo = FALSE, fig.height = 10}
library(tidyverse)
library(lubridate)
library(gghighlight)
library(ungeviz)
library(dviz.supp)
theme_set(theme_minimal(15))

crime <- read_csv(here::here("data", "crime.csv")) %>% 
  janitor::clean_names()

crime %>% 
  filter(is_crime == 1) %>% 
  mutate(offense_category_id = str_to_title(
    str_replace_all(offense_category_id, "-", " "))
  ) %>% 
  group_by(offense_category_id) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n),
         se = sqrt((prop*(1-prop)) / n),
         lower = prop + qnorm(0.025)*se,
         lower = ifelse(lower < 0, 0, lower),
         upper = prop + qnorm(0.975)*se) %>% 
  ggplot(aes(fct_reorder(offense_category_id, prop), prop)) +
    geom_errorbar(aes(ymin =lower, ymax = upper),
                  width = 0.3,
                  color = "gray40") +
    geom_point(color = "#4375D3",
               size = 2) +
    coord_flip(expand = FALSE) +
    scale_y_continuous("Percentage", 
                       labels = scales::percent,
                       limits = c(-0.01, .305),
                       breaks = seq(0, .3, .1)) +
    labs(x = "",
         caption = "Denver Crime Data Distributed via Kaggle\nhttps://www.kaggle.com/paultimothymooney/denver-crime-data",
         title = "Crimes in Denver") 
``` 

2. Visualize the same relation, but displaying the uncertainty using an alternative method of your choosing.

```{r viz2, eval = FALSE}
crime %>% 
  filter(is_crime == 1) %>% 
  mutate(offense_category_id = str_to_title(
    gsub("-", " ", offense_category_id))) %>% 
  group_by(offense_category_id) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n),
         se = sqrt((prop*(1-prop)) / n),
         lower = prop + qnorm(0.025)*se,
         lower = ifelse(lower < 0, 0, lower),
         upper = prop + qnorm(0.975)*se,
         offense_category_id = fct_reorder(offense_category_id, prop)) %>% 
  ggplot(aes(prop, offense_category_id)) +
    stat_confidence_density(aes(moe = se), 
                            fill = "#4375D3", 
                            confidence = pnorm(.5)) +
    geom_segment(aes(y = as.numeric(offense_category_id) - 0.4, 
                     yend = as.numeric(offense_category_id) + 0.4, 
                     x = prop, xend = prop),
                 color = "#F0FF00",
                 size = 1.1) +
    coord_cartesian(expand = FALSE) +
    scale_x_continuous("Percentage", 
                       labels = scales::percent,
                       limits = c(-0.01, .305),
                       breaks = seq(0, .3, .1)) +
    labs(y = "",
         caption = "Denver Crime Data Distributed via Kaggle\nhttps://www.kaggle.com/paultimothymooney/denver-crime-data",
         title = "Crimes in Denver") 
```

3. Reproduce the following plot. Use the `reported_date` to extract the year.

```{r viz3}
smry <- crime %>% 
  separate(reported_date, c("date", NA, NA), sep = " ") %>% 
  mutate(year = year(mdy(date))) %>% 
  group_by(year, district_id) %>% 
  count() %>% 
  group_by(year) %>% 
  mutate(prop = n/sum(n),
         se = sqrt((prop*(1-prop)) / n),
         lower = prop + qnorm(0.025)*se,
         lower = ifelse(lower < 0, 0, lower),
         upper = prop + qnorm(0.975)*se) %>% 
  ungroup() %>% 
  mutate(district_id = fct_reorder(factor(district_id), prop),
         year = factor(year))

ggplot(smry, aes(district_id, prop)) +
  geom_col(aes(fill = district_id)) +
  geom_errorbar(aes(ymin = lower, ymax = upper),
                width = 0.4,
                color = "gray40") +
  facet_wrap(~year) +
  coord_flip() +
  scale_x_discrete("District") +
  scale_fill_OkabeIto() +
  scale_y_continuous("Proportion", limits = c(0, 0.25), breaks = seq(0, .3, .1)) +
  guides(fill = "none") +
  labs(caption = "Denver Crime Data Distributed via Kaggle\nhttps://www.kaggle.com/paultimothymooney/denver-crime-data",
       title = "Crimes in Denver") 

```


4. Limit your data to the following. Note that only rows corresponding to a crime have been retained, and I have counted the number of rows (crimes) for each district in each year. I have stored this data frame in an object called `counts`

```{r subset}
counts <- crime %>% 
  filter(is_crime == 1) %>% 
  separate(reported_date, c("date", NA, NA), sep = " ") %>% 
  mutate(year = year(mdy(date))) %>% 
  count(year, district_id)
counts
```

Fit the following model
```{r model, echo = TRUE}
m <- glm(n ~ I(factor(district_id)) + I(year - 2014), 
         data = counts)
```

Extract the output using `broom::tidy`

```{r tidy, echo = TRUE}
tidied <- broom::tidy(m)
```

Divide the probability space, `[0, 1]`, into even bins of your choosing. For example, for 20 bins I could run the following

```{r ppoints, echo = TRUE}
ppoints(20)
```


The coefficients (`tidied$estimate`) for each district in the model represent the difference in crime rates between the corresponding district (the integer at the end of `tidied$term`) and District 1 in 2014. For example, District 2 had an estimated `r round(abs(tidied$estimate[2]))` fewer crimes than District 1. However, there is uncertainty in this estimate, with a standard error of `r round(tidied$std.error[2], 2)`. The point estimate for a given district represents our "best guess" as to the true difference, and the likelihood of alternative differences are distributed around this point with a standard deviation equal to the standard error. We can simulate data from this distribution, if we choose, or instead just use the distribution to calculate different quantiles.  

The `qnorm` function transforms probabilities, such as those we generated with `ppoints`, into values according to some pre-defined normal distribution (by default $\mu = 0, \sigma = 1$). For example `qnorm(.75, mean = 100, sd = 10)` provides the 75th percentile value from a distribution with a mean of 100 and a standard deviation of 10. We can therefore use `qnorm` in conjunction with `ppoints` to better understand the sampling distribution and, ultimately, communicate uncertainty. For example the following code generates the values corresponding to `ppoints(20)`, or 2.5th to 97.5th percentiles of the distributions in 5 percentile "jumps", for the difference in crime rates for District 1 and 2.

```{r qnorm, , echo = TRUE}
qnorm(ppoints(20), 
      mean = tidied$estimate[2],
      sd = tidied$std.error[2])
```


Using this procedure, replicate a plot like the following, but displaying the likelihood of the crime rate differences between District 4 and District 1 (e.g., you will need to use `tidied$estimate[4]` and `tidied$std.error[4]`). Make sure to put the values in a data frame, and create a  new variable stating whether the difference is greater than zero (which you will use to fill by).

**Note:** Your probabilities will not directly correspond with the $p$ values, which are essentially twice the probability you are displaying (because the test is two-tailed).

```{r dotplot, fig.height = 7}
diff_dist_12 <- data.frame(balls = qnorm(ppoints(20), 
                                         tidied$estimate[2], 
                                         tidied$std.error[2])) %>% 
  mutate(higher_crime = ifelse(balls < 0, "District 2", "District 1"))


ggplot(diff_dist_12, aes(balls)) +
  geom_dotplot(aes(fill = higher_crime), binwidth = 1050) +
  scale_fill_OkabeIto(name = "Higher Crime") +
  scale_y_continuous("", breaks = NULL, limits = c(0, 1.5)) +
  scale_x_continuous("Difference in total number of crimes", 
                     breaks = seq(-8000, 3000, 1500)) +
  geom_vline(xintercept = 0, color = "#D04343", size = 2) +
  labs(title = "Difference in total number of crimes",
       subtitle = "District 2 Crimes - District 1 Crimes", 
       caption = "Each ball represents 5% probability") +
  guides(fill = "none") +
  annotate("text", -4000, 0.9, label = "District 2", size = 10, color = "gray40") +
  annotate("text", 1500, 0.9, label = "District 1", size = 10, color = "gray40")
```

5. Reproduce the following table

```{r tbl}
library(gt)
crime %>% 
  filter(offense_category_id == "aggravated-assault" |
           offense_category_id == "murder" |
           offense_category_id == "sexual-assault" |
           offense_category_id == "other-crimes-against-persons") %>% 
  filter(district_id %in% c(1, 3, 5)) %>% 
  mutate(offense_category_id = str_replace_all(offense_category_id, "-", " "),
         offense_category_id = str_to_title(offense_category_id), 
         offense_category_id = factor(offense_category_id,
                                      levels = c("Aggravated Assault",
                                                 "Sexual Assault", 
                                                 "Murder",
                                                 "Other Crimes Against Persons"))) %>% 
  separate(reported_date, c("date", NA, NA), sep = " ") %>% 
  mutate(year = year(mdy(date))) %>% 
  count(offense_category_id, district_id, year) %>% 
  mutate(district_id = paste0("District ", district_id)) %>% 
  spread(year, n, fill = 0) %>% 
  group_by(district_id) %>% 
  gt() %>% 
  tab_spanner("Year", columns = vars(2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  cols_align(align = "left", columns = vars(offense_category_id)) %>% 
  cols_label(offense_category_id = "Offense") %>% 
  tab_header(title = "Crimes Against Persons in Denver: 2014 to Present",
             subtitle = md("*Sample of three districts*")) %>% 
  tab_source_note(source_note = md("Denver Crime Data Distributed via [Kaggle](https://www.kaggle.com/paultimothymooney/denver-crime-data)"))
```
