---
title: "Lab 1"
subtitle: "Collaborating on GitHub"
date: "Assigned 1/9/19, Due 1/14/19"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: "journal"
    css: "website-custom.css"
---

```{r setup, include=FALSE}
library(tufte)

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = FALSE,
                      fig.width = 10,
                      fig.height = 10)

```

# Overview
The purpose of this lab is to get your working with *git* and *GitHub*
collaboratively. You should work together in groups of 3-4. At least one
person from the group should have prior experience with *git/GitHub*. The basics
of the lab are to:

* Create a shared repo
* Create an R Markdown document
* Work on a few different data visualizations together
  + Different people make different commits
* Submit a link to the repo through Canvas when you've completed the lab
* I check the commit history, and give each person credit

## Data
We'll work with Week 1 of the [#tidytuesday](https://twitter.com/search?q=%23tidytuesday&src=tyah) 
data for 2019, specificially the 
[#rstats](https://twitter.com/search?q=%23rstats&src=typd)
dataset containing nearly 500,000 tweets over a little more than a decade using
that hashtag. 

# Commits {.tabset}

Glance through the commits below. Each person should be responsible for at least
one commit. Commit 1 must be completed first. However, please work on Commit 2
and Commit 4 simultaneously (one person working on each commit). Commits 3/5
cannot be completed until after Commits 2/4, respectively.

**Note:** You may end up with a merge conflict. That's okay, we're here to 
practice. I like [gitkraken](https://www.gitkraken.com) for managing merge
conflicts, but you can use whatever works best for you.

## Commit 1

* Create a shared GitHub repo
* Create an RStudio project
* Create a folder in the repo called "data" and place the corresponding data there
* Initialize a new R Markdown document
* Load the data

```{r fig.fullwidth = TRUE, fig.width = 10, fig.height = 10, echo = FALSE}
library(tidyverse)
library(rio)
d <- import(here::here("data", "rstats_tweets.rds"),
            setclass = "tbl_df") 
```

## Commit 2

* Create the following figure. Some guidance:
  + You'll want to count the number of times a screen name appears and select
    only the top 25.
    - Consider using arranging in descending order, then using `dplyr::slice`
  + Make the screen name a factor, ordered according to the number of times
    it appears.
    - Consider `forcats::fct_reorder`
  + `coord_flip` will be your friend here

```{r fig1-raw}
d %>% 
  count(screen_name, sort = TRUE) %>% 
  slice(1:25) %>% 
  mutate(screen_name = fct_reorder(factor(screen_name), n)) %>% 
  ggplot(aes(screen_name, n)) +
  geom_col() +
  coord_flip() 
```

## Commit 3
* Style the plot so it matchest the below. 
  + Use `theme_minimal`
  + Use `"cornflowerblue"`
  + Increase the `base_size`
  + set the `fig.width` and `fig.height` to 10

```{r fig1-styled}
d %>% 
  count(screen_name, sort = TRUE) %>% 
  slice(1:25) %>% 
  mutate(screen_name = fct_reorder(factor(screen_name), n)) %>% 
  ggplot(aes(screen_name, n)) +
  geom_col(alpha = 0.7,
           fill = "cornflowerblue") +
  coord_flip() +
  labs(x = "Twitter Screen Name",
       y = "Count",
       title = "Most prolific #rstats tweeters",
       subtitle = "Top 25 screen names displayed",
       caption = "Data from Mike Kearny, distributed via #tidytuesday") +
  theme_minimal(base_size = 20)
```


## Commit 4
* Create the following figure. Some guidance:
  + First create a `month` variable that rounds the `created_at` variable to 
    the nearest month. You might consider looking at `lubridate::round_date`.
  + Restrict the count to prior to 2019. I would recommend using 
    `lubridate::as_datetime("2019-01-01 00:00:00")`
  + Count the number of rows (tweets) in the dataset for each month

```{r fig2-raw}
library(lubridate)
d %>% 
  mutate(month = round_date(created_at, unit = "month")) %>% 
  count(month) %>%
  filter(month < lubridate::as_datetime("2019-01-01 00:00:00")) %>% 
  ggplot(aes(month, n)) +
  geom_smooth() +
  geom_line() 
```

## Commit 5
* Style the plot so it matchest the below. 
  + Use `theme_minimal`
  + Use `"gray80"` and `"cornflowerblue"`
  + Increase the `base_size`
  + set the `fig.width` and `fig.height` to 10

```{r fig2-styled}
d %>% 
  mutate(month = round_date(created_at, unit = "month")) %>% 
  count(month) %>%
  filter(month < lubridate::as_datetime("2019-01-01 00:00:00")) %>% 
  ggplot(aes(month, n)) +
  geom_line(lwd = 1.5, 
            color = "gray80") +
  geom_smooth(color = "cornflowerblue",
              lwd = 1.2,
              se = FALSE) +
  labs(x = "Year (data summarized by month)",
       y = "Number of #rstats tweets",
       title = "Growth of the #rstats hashtag on twitter over time",
       caption = "Data from Mike Kearny, distributed via #tidytuesday") +
  theme_minimal(base_size = 20)
```